### 2015-07-12 thesis/thesis/chap1/chap1.tex
changes

Within communities, services can exhibit competitive behavior as they provide the same functionalities and the number of users requests is finite.
However, for the same reason of being functionally similar, services can cooperate with each other, for example to substitute each other in order to perform some sub-tasks.
For instance, services can opt for performing tasks if they feel they are capable enough
or decide to cooperate by showing the availability to perform some sub-tasks. The relevant question to be addressed is: \emph{How can we design a community model where both competitive and cooperative behaviors exist? [R4]}

In most of the recent work on communities of web service, the solutions consider the architecture of centralized management for communities where most of the decisions are made by the centralized coordinator. However, in real world scenarios, decisions made by independent service providers are highly distributed.  \emph{How can we model a distributed decision making process for the problem of forming communities of services? [R5]}

Also in all of the mentioned proposals, the community manager as a centralized entity, has complete information of all the web services and their quality. However, centrality and complete information are strong assumptions, which are not fully compatible with real business scenarios.
\emph{How can we train web services based on limited information to operate efficiently? [R6]}

@@

\section{Thesis Organization}\label{sec:outline}
The rest of the proposal is organized as follows: We present in Chapter 2 the background needed for our research along with relevant related work. Chapter 3 provides an efficient method of coalition formation for web services. In Chapter 4 we discuss the cooperative behaviour within the communities of web services. Chapter 5 presents a distributed method of formation of web services communities. Finally in Chapter 6, we present our conclusion and future plan.

>>>>

In most of the recent work on communities of web service, the solutions consider the architecture of centralized management for communities where most of the decisions are made by the centralized coordinator. However, in real world scenarios, decisions made by independent service providers are highly distributed.  \emph{How can we model a distributed decision making process for the problem of forming communities of services? [R4]}

Also in all of the mentioned proposals, the community manager as a centralized entity, has complete information of all the web services and their quality. However, centrality and complete information are strong assumptions, which are not fully compatible with real business scenarios.
\emph{How can we train web services based on limited information to operate efficiently? [R5]}

Within communities, services can exhibit competitive behavior as they provide the same functionalities and the number of users requests is finite.
However, for the same reason of being functionally similar, services can cooperate with each other, for example to substitute each other in order to perform some sub-tasks.
For instance, services can opt for performing tasks if they feel they are capable enough
or decide to cooperate by showing the availability to perform some sub-tasks. The relevant question to be addressed is: \emph{How can we design a community model where both competitive and cooperative behaviors exist? [R6]}

@@

\section{Thesis Organization}\label{sec:outline}
The rest of the proposal is organized as follows: We present in Chapter 2 the background needed for our research along with relevant related work. We introduce the web services and the concept of communities of web services and the theoretical background used throughout the these. Chapter 3 provides an efficient method of coalition formation for web services. In this chapter we have addressed $[R1]$, $[R2]$, $[R3]$ research questions on efficient ways of community formation.  Chapter 4 presents a distributed method of formation of web services communities. In this chapter we address $[R4]$, $[R5]$ research questions by proposing DDM, a distributed decision making mechanism for our web services which can perform in distributed manner and when information is incomplete. In Chapter 5 we delve into internal management of communities of web services and we address the $[R6]$ research question by analyzing the cooperative behaviour within the communities of web services. Finally in Chapter 6, we present our conclusion and future plan.

### 2015-07-12 thesis/thesis/chap2/chap2.tex
changes

\subsection{Web Services}\label{sec:CWSWebServices}
Over the past years, online services have become part of standard
daily life of people around the globe. Many modern applications
rely on web services from different providers. For instance, many
mobile and tablet applications which have limited storage and
processing power are merely interfaces aggregating different
information from online services. Examples are vast, weather
forecasting, ticket selling, shopping apps, local maps and places
searching.

@@

Cooperative game is a branch of game theory that studies
strategies of self-interested entities or agents in a setting
where those agents can increase their payoff by binding agreements
and cooperating in groups. We let $N$ be a set of players which
can form a group called a $coalition$. A \emph{coalitional game}
is a pair $G = (N, v)$, where $v$ is called a \emph{characteristic
function} $v: 2^N \to \mathbb{R}$, mapping the set of players of
the coalition to a real number $v(N)$, the worth of $N$. This
number usually represents the output or payoff or again the
performance of these players working together as coalition. If a
coalition $S$ is formed, then it can divide its worth, $v(N)$ in
any possible way among its members. The payoff vector $x \in
\mathbb{R}^N$ is the amount of payoff being distributed among the
members of the coalition $N$. The payoff vector satisfies two
conditions:

@@

        The second criteria is called the \emph{feasibility} condition,
        according to which, the payoff for each agent cannot be more than
        the coalition total gain. A payoff vector is also \emph{efficient}
        if the payoff obtained by a coalition is distributed amongst the
        coalition members: $\sum_{i \in N} x_i = v(N)$. This definition of
        the characteristic function works in \emph{transferable utility}
        (TU) settings, where utility (i.e., payoff) is transferable from
        one player to another, or in other words, players have common
        currency and a unit of income that is worth the same for all players
        \cite{myerson1991game}.

@@

            \subsubsection*{$\epsilon$-core}\label{s:epsilon}
            %\emph{$\epsilon$-Core:}
            %\\
            When the \emph{core} set of a game is empty, it means no coalition
            of players can gain anything by deviating. An outcome would be
            unstable if a coalition can benefit even by a small amount from
            deviating, which is a strong requirement. In fact, in some
            situations, deviations can be costly, or players may have loyalty
            to their coalitions, or even it can be computationally intractable
            to find those small benefits. It would only make sense for a
            coalition to deviate if the gain from a deviation exceeds the cost
            of performing the deviation. \emph{$\epsilon$-core} relaxes the
            notion of the core, and only requires that no coalition would
            benefit significantly, or within a constant amount($\epsilon$) by
            deviating (see Equation \ref{eq:core}).

@@

        Core stability is a highly desirable property however in many problems it is not achievable. It would be more ideal to maintain a set of somewhat stable payoffs when the core is empty. There are several approaches to achieve this goal. One may drop the stability requirement and focus on other types of solutions for which a payoff division is guaranteed to exist. Two well known solution concepts in this category are \emph{nucleolus}\cite{schmeidler_nucleolus_1969} and the \emph{bargaining set}\cite{Davis67existenceof}. They try to minimize some measure of unhappiness in the game for the agents.

@@

        A community can also be stabilized by relaxing the core constraints. According to \emph{Core}, an outcome is unstable if a coalition can benefit even by a small amount from deviating, which is a strong requirement. In fact, in some situations, deviations can be costly, or players may have loyalty to their coalitions, or even it can be computationally intractable to find those small benefits. It would only make sense for a coalition to deviate if the gain from a deviation exceeds the cost of performing the deviation. \emph{$\epsilon$-core} relaxes the notion of the core, and only requires that no coalition would benefit significantly, or within a constant amount($\epsilon$) by deviating (see Equation \ref{eq:core}).

@@

In \cite{DBLP:journals/internet/BenatallahSD03}, Benatallah et al.
defined communities as \emph{Service Containers} that aggregate
substitutable web services providing a common functionality (same
set of operations). They abstracted \emph{Service Containers} as
web services that are created, advertised, discovered and invoked
just as elementary web services. The \emph{Container} is
considered as a manager that is responsible for web service
selection upon receiving a request on run-time. The authors have
proposed a scoring service based on non-functional requirements of
the request and web service capabilities to dynamically chose the
web service to perform the requested task. A similar concept was
proposed by Maamar et al. in
\cite{DBLP:journals/ijebr/MaamarSTBB09}. The authors introduced
web service communities as a collection of web services with a
common functionality but different QoS properties. A community
manager, upon receiving a request, delegates the request to one of
its current members. The choice is based on the performance
history and quality metrics of each web service. The authors have
proposed an efficient global web service selection algorithm in
order to approach quality constraints and preferences for
composite services which require aggregation of different types of
services to satisfy the user.

@@

In \cite{10.1109/TSC.2012.12}, a cooperative scheme among
autonomous web services based on coalitional game theory has been
introduced. The authors have proposed an interesting algorithm to
reach individually stable coalition partition for web services in
order to maximize their efficiency. The communities choose new web
services on the promise that it would benefit the community
without decreasing any other web service's income. In the proposed
model, the worth of community is evaluated with high emphasis on
the availability metric and considering price and cost values
only. The community structure is based on a coordination chain,
where a web service is considered as a \emph{primary} web service
and the community task-distribution method initially invokes the
primary web service and only if the primary web service is
unavailable, the method invokes the next backup web services as
they are ordered in the coordination chain. We believe that this
coordination chain limits the cooperation power as it introduces a
sort of hierarchy. However, in pure and open cooperative models,
such as the one we propose in this paper, active cooperation
activities engaging simultaneously many agents so that they can
perform the tasks more efficiently are being used. Moreover, if
the availability is high, which is the case nowadays with the
recent advancements in cloud and hardware infrastructures, the
backup web services will end-up having a very low chance of
getting jobs, especially the ones further in the chain. This will
results in a considerable waste of web services capabilities.

@@

At the best of our knowledge, there is no work in the literature of service and agent computing addressing the issue of coopetition strategies and when to cooperate or to compete. However, some relevant proposals to our proposed model are the ones that address service selection and task allocation mechanisms. In many frameworks proposed in the literature, service selection and task allocation are regulated based on the reputation parameter \cite{Bentahar:2012:ARA:2343124.2343267,DBLP:journals/jwsr/RosarioBJ10,Ruth_Tu_2007-7,journals/kbs/Yahyaoui12}. In \cite{HuangCommunications}, the authors propose a framework to match potential benefits of services while cooperating with one another. The interesting idea is to consider the benefits under four categories: innovation and learning, internal business process, customer, and financial benefits. Innovation and learning perspective focuses on the knowledge, skills, and systems needed to improve the business continually. Necessary factors to build strategic capabilities and efficiency in addressed in internal business process. Values that customers seek are considered in \emph{customer perspective} and financial performance to maximize the shareholder value are analyzed in \emph{financial perspective}. Their goal is to design the framework for cooperating web services, inline with business strategy of firms in IT industry. In \cite{alchieri:a}, the authors present a dependable framework for cooperative service agents that is based on the tuple space coordination model. The intrusion-tolerant perspective is emphasized in this paper where several security mechanisms are developed to enable a reliable coordination system. %In \cite{Maximilien2}, authors propose %ontology for quality of service. Users compute the web services' %reputation using ratings.
The proposed frameworks mostly aim to facilitate the coordination mechanism between services. However, the opposite strategy of competing is not analyzed where services might be more successful when competing within the same group. In fact, services are not always willing to cooperate even if they have some common goals, particularly when they operate within groups such as communities. In such a context, service agents can follow different interacting strategies and have to decide when to compete and when to cooperate so that their ultimate goal, maximizing their incomes, can be better achieved. In our framework, we analyze those different strategies to help services in their decision making process when these
agents function within communities. 
%We summarize most of %these proposals and concentrate on strategic decision making %system that ranks web services in the community and analyze their %effective interacting strategies to accomplish continuous %requested tasks.
We enable service agents to reasonably evaluate and decide over their coopetition strategies, which means deciding when to compete and when to cooperate.

@@

In this research work, as the first contribution we will tackle with the issue of community formation in an efficient way for all the web service and communities involved. We will use game theory to propose a cooperative game model for the aggregation of web services within communities. The solution concepts of our cooperative game seeks to find efficient ways of forming coalitions (teams) of web services so that they can maximize their gain and payoff, and distribute the gain in a fair way among all the web services. Achieving Fairness when the gain is distributed among the community members is the main factor to keep the coalition stable as no web service will expect to gain better by deviating from the community. In other words, the coalition is made efficient if all the members are satisfied. We first propose a representation function for communities of web services based on their QoS attributes. By using this function, we can evaluate the $worth$ of each community of web services. When facing new membership requests, a typical community master checks whether the new coalition having the old and new set of web services will keep the community stable or not. The community master will reject the membership requests if it finds out that the new coalition would be unstable, preventing $any$ subset of web services from gaining significantly more by deviating from the community and joining other communities or forming new ones. The computation of solutions for cooperative game theory problems is combinatorial in nature and proven to be NP-complete \cite{Algorithmic}, making this computation impractical in real world applications. However, using the concepts of coalition stability, we propose approximation algorithms running in polynomial time providing web services and community masters with applicable and near-optimal decision making mechanisms.

>>>>

\subsection{Web Services}\label{sec:CWSWebServices}
Over the past years, online services have become part of standard
daily life of people around the globe. Many modern applications
rely on web services from different providers. For instance, many
mobile and tablet applications which have limited storage and
processing power are merely interfaces aggregating different
information from online services. Examples are vast, weather
forecasting, ticket selling, shopping apps, local maps and places
searching are some of them.

@@

The theory of cooperative games is a branch of game theory that is a branch of game theory that studies
strategies of self-interested entities or agents in a setting
where those agents can increase their payoff by binding agreements
and cooperating in groups. We let $N$ be a set of players which
can form a group called a $coalition$. A \emph{coalitional game}
is a pair $G = (N, v)$, where $v$ is called a \emph{characteristic
function} $v: 2^N \to \mathbb{R}$, mapping the set of players of
the coalition to a real number $v(N)$, the worth of $N$. This
number usually represents the output or payoff or again the
performance of these players working together as coalition. If a
coalition $S$ is formed, then it can divide its worth, $v(N)$ in
any possible way among its members. The payoff vector $x \in
\mathbb{R}^N$ is the amount of payoff being distributed among the
members of the coalition $N$. The payoff vector satisfies two
conditions:

@@

        The second criterion is called the \emph{feasibility} condition,
        according to which, the payoff for each agent cannot be more than
        the coalition total gain. A payoff vector is also \emph{efficient}
        if the payoff obtained by a coalition is distributed amongst the
        coalition members: $\sum_{i \in N} x_i = v(N)$. This definition of
        the characteristic function works in \emph{transferable utility}
        (TU) settings, where utility (i.e., payoff) is transferable from
        one player to another, or in other words, players have common
        currency and a unit of income that is worth the same for all players
        \cite{myerson1991game}.

@@

            \subsubsection*{$\epsilon$-core}\label{s:epsilon}
            %\emph{$\epsilon$-Core:}
            %\\
            When the \emph{core} set of a game is empty, it means no coalition
            of players can gain anything by deviating. An outcome would be
            unstable if a coalition can benefit even by a small amount from
            deviating, which is a strong requirement. In fact, in some
            situations, deviations can be costly, or players may have loyalty
            to their coalitions, or even it can be computationally intractable
            to find those small benefits. It would only make sense for a
            coalition to deviate if the gain from a deviation exceeds the cost
            of performing the deviation. \emph{$\epsilon$-core} relaxes the
            notion of the core, and only requires that no coalition would
            benefit significantly, or within a constant amount($\epsilon$) by
            deviating (see Equation \ref{eq:core2}).

@@

        Core stability is a highly desirable property however in many problems it is not achievable. It would be more ideal to maintain a set of somewhat stable payoffs when the core is empty. There are several approaches to achieve this goal. One may drop the stability requirement and focus on other types of solutions for which a payoff division is guaranteed to exist. Two well known solution concepts in this category are \emph{nucleolus} \cite{schmeidler_nucleolus_1969} and the \emph{bargaining set} \cite{Davis67existenceof}. They try to minimize some measure of unhappiness in the game for the agents.

@@

        A community can also be stabilized by relaxing the core constraints. According to \emph{Core}, an outcome is unstable if a coalition can benefit even by a small amount from deviating, which is a strong requirement. In fact, in some situations, deviations can be costly, or players may have loyalty to their coalitions, or even it can be computationally intractable to find those small benefits. It would only make sense for a coalition to deviate if the gain from a deviation exceeds the cost of performing the deviation. \emph{$\epsilon$-core} relaxes the notion of the core, and only requires that no coalition would benefit significantly, or within a constant amount($\epsilon$) by deviating (see Equation \ref{eq:core3}).

           \begin{equation}\label{eq:core3}
               \forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S) - \epsilon
           \end{equation}

@@

Here we introduce the related research work regarding the engineering and formation
of communities of web services. In \cite{DBLP:journals/internet/BenatallahSD03}, Benatallah et al.
defined communities as \emph{Service Containers} that aggregate
substitutable web services providing a common functionality (same
set of operations). They abstracted \emph{Service Containers} as
web services that are created, advertised, discovered and invoked
just as elementary web services. The \emph{Container} is
considered as a manager that is responsible for web service
selection upon receiving a request on run-time. The authors have
proposed a scoring service based on non-functional requirements of
the request and web service capabilities to dynamically chose the
web service to perform the requested task. A similar concept was
proposed by Maamar et al. in
\cite{DBLP:journals/ijebr/MaamarSTBB09}. The authors introduced
web service communities as a collection of web services with a
common functionality but different QoS properties. A community
manager, upon receiving a request, delegates the request to one of
its current members. The choice is based on the performance
history and quality metrics of each web service. The authors have
proposed an efficient global web service selection algorithm in
order to approach quality constraints and preferences for
composite services which require aggregation of different types of
services to satisfy the user.

@@

In \cite{10.1109/TSC.2012.12}, a cooperative scheme among
autonomous web services based on coalitional game theory has been
introduced. The authors have proposed an interesting algorithm to
reach individually stable coalition partition for web services in
order to maximize their efficiency. The communities choose new web
services on the promise that it would benefit the community
without decreasing any other web service's income. In the proposed
model, the worth of community is evaluated with high emphasis on
the availability metric and considering price and cost values
only. The community structure is based on a coordination chain,
where a web service is considered as a \emph{primary} web service
and the community task-distribution method initially invokes the
primary web service and only if the primary web service is
unavailable, the method invokes the next backup web services as
they are ordered in the coordination chain. We believe that this
coordination chain limits the cooperation power as it introduces a
sort of hierarchy. However, in pure and open cooperative models,
such as the one we propose in this thesis, active cooperation
activities engaging simultaneously many agents so that they can
perform the tasks more efficiently are being used. Moreover, if
the availability is high, which is the case nowadays with the
recent advancements in cloud and hardware infrastructures, the
backup web services will end-up having a very low chance of
getting jobs, especially the ones further in the chain. This will
results in a considerable waste of web services capabilities.

@@

At the best of our knowledge, there is no work in the literature of service and agent computing addressing the issue of coopetition strategies and when to cooperate or to compete. However, some relevant proposals to our proposed model are the ones that address service selection and task allocation mechanisms. In many frameworks proposed in the literature, service selection and task allocation are regulated based on the reputation parameter \cite{Bentahar:2012:ARA:2343124.2343267,DBLP:journals/jwsr/RosarioBJ10,Ruth_Tu_2007-7,journals/kbs/Yahyaoui12}. In \cite{HuangCommunications}, the authors propose a framework to match potential benefits of services while cooperating with one another. The interesting idea is to consider the benefits under four categories: innovation and learning, internal business process, customer, and financial benefits. Innovation and learning perspective focuses on the knowledge, skills, and systems needed to improve the business continually. Necessary factors to build strategic capabilities and efficiency in addressed in internal business process. Values that customers seek are considered in \emph{customer perspective} and financial performance to maximize the shareholder value are analyzed in \emph{financial perspective}. Their goal is to design the framework for cooperating web services, inline with business strategy of firms in IT industry. In \cite{alchieri:a}, the authors present a dependable framework for cooperative service agents that is based on the tuple space coordination model. The intrusion-tolerant perspective is emphasized in the paper where several security mechanisms are developed to enable a reliable coordination system. %In \cite{Maximilien2}, authors propose %ontology for quality of service. Users compute the web services' %reputation using ratings.
The proposed frameworks mostly aim to facilitate the coordination mechanism between services. However, the opposite strategy of competing is not analyzed where services might be more successful when competing within the same group. In fact, services are not always willing to cooperate even if they have some common goals, particularly when they operate within groups such as communities. In such a context, service agents can follow different interacting strategies and have to decide when to compete and when to cooperate so that their ultimate goal, maximizing their incomes, can be better achieved. In our framework, we analyze those different strategies to help services in their decision making process when these
agents function within communities.
%We summarize most of %these proposals and concentrate on strategic decision making %system that ranks web services in the community and analyze their %effective interacting strategies to accomplish continuous %requested tasks.
We enable service agents to reasonably evaluate and decide over their coopetition strategies, which means deciding when to compete and when to cooperate.

@@

In this thesis, as the first contribution, we will tackle the issue of community formation in an efficient way for all the web services and communities involved. We will use game theory to propose a cooperative game model for the aggregation of web services within communities. The solution concepts of our cooperative game seeks to find efficient ways of forming coalitions (teams) of web services so that they can maximize their gain and payoff, and distribute the gain in a fair way among all the web services. Achieving fairness when the gain is distributed among the community members is the main factor to keep the coalition stable as no web service will expect to gain better by deviating from the community. In other words, the coalition is made efficient if all the members are satisfied. We first propose a representation function for communities of web services based on their QoS attributes. By using this function, we can evaluate the $worth$ of each community of web services. When facing new membership requests, a typical community master checks whether the new coalition having the old and new set of web services will keep the community stable or not. The community master will reject the membership requests if it finds out that the new coalition would be unstable, preventing $any$ subset of web services from gaining significantly more by deviating from the community and joining other communities or forming new ones. The computation of solutions for cooperative game theory problems is combinatorial in nature and proven to be NP-complete \cite{Algorithmic}, making this computation impractical in real world applications. However, using the concepts of coalition stability, we propose approximation algorithms running in polynomial time providing web services and community masters with applicable and near-optimal decision making mechanisms.

### 2015-07-12 thesis/thesis/chap3/chap3.tex
changes

\subsection{Coopetitive Behavior}\label{sb:resutlscoop}

@@

In this section, we proposed a cooperative game theory-based model for the aggregation of web services within communities. The goal of our services is to maximize efficiency by collaborating and forming stable coalitions. Our method considers stability and fairness for all web services within a community and offers an applicable mechanism for membership requests and selection of web services. The ultimate goal is to increase revenue by improving user satisfaction, which comes from the ability to perform more
tasks with high quality. Simulation results show that our, polynomial in complexity, approximation algorithms provide web services and community owners with applicable and near-optimal
decision making mechanisms.

As future work in this area, we would like to perform more analytical and theoretical analysis on the convexity condition and also minimal $\epsilon$ values in \emph{$\epsilon$-core} solution concepts based on the characteristic function in web service applications. From web service perspective, the work can be extended to consider web service compositions where a group of web services having different set of skills cooperate to perform composite tasks. Also bargaining theory from cooperating game theory concepts can be used to help web services resolve the instability and unfairness issues by side payments.

In this chapter, we assumed our web services and communities have compelte knowledge of all the other web services and their parameters. In next section we propose distributed decision making model which can perform in scenarios where information is incomplete.

>>>>

@@

In this chapter, we proposed a cooperative game theory-based model for the aggregation of web services within communities. The goal of our services is to maximize efficiency by collaborating and forming stable coalitions. Our method considers stability and fairness for all web services within a community and offers an applicable mechanism for membership requests and selection of web services. The ultimate goal is to increase revenue by improving user satisfaction, which comes from the ability to perform more
tasks with high quality. Simulation results show that our, polynomial in complexity, approximation algorithms provide web services and community owners with applicable and near-optimal
decision making mechanisms.

%As future work in this area, we would like to perform more analytical and theoretical analysis on the convexity condition and also minimal $\epsilon$ values in \emph{$\epsilon$-core} solution concepts based on the characteristic function in web service applications. From web service perspective, the work can be extended to consider web service compositions where a group of web services having different set of skills cooperate to perform composite tasks. Also bargaining theory from cooperating game theory concepts can be used to help web services resolve the instability and unfairness issues by side payments.

In this chapter, we assumed our web services and communities have compelte knowledge of all the other web services and their parameters. In next chapter we propose distributed decision making model which can perform in scenarios where information is incomplete.

### 2015-07-12 thesis/thesis/chap4/chap4.tex
changes

Over the past years, online services have become an important part of many scalable business applications. The increasing reliance on online service providers has significantly influenced the way web services are engineered. Given the dynamic and unpredictable nature of the Internet, delivering high quality services is still a critical and challenging issue. One practical solution towards delivering such quality services is utilizing intelligent decision making agents. These agents aim at maximizing their gain by exploring the best ways to provide services that satisfy end users \cite{Zeng:2003:QDW:775152.775211, 10.1109/ARES.2008.7, Demirkan2013412, journals/tsc/ZhengZYB13, Josang:2007:STR:1225318.1225716}. However, agent-based web services are functionally limited in the sense that they cannot handle a large number of requests at the same time without compromising the quality of service provided. Recent developments have attempted to shift web services from simple models, consisting of individual components, to models made up of autonomous and group-based components that share common goals. In group-based models, interaction, composition, and cooperation are the key challenges that directly impact the group's overall performance in achieving common goals \cite{ICWS2011-1, SCC2011-1, journals/mags/BaldoniBM10, journals/jcss/CasadoYT13}. To that end, we see the emergence of web service \emph{communities}, which consist of grouping services with similar functionalities but distinct nonfunctional properties \cite{Zeng:2003:QDW:775152.775211, 10.1109/ARES.2008.7, Paik:2005:TSS:2229263.2230038, Medjahed05adynamic}. A community of web services runs continuous performance assessment functions that regulate web services' interactions and manage their composition and cooperation.

@@

\section{Preliminaries and Challenging Issues}\label{s4:preliminaries}
%In this section, we first present the architecture of DDM. We explore the characteristics of intelligent service agents and the features we extract for training. To do this, we first discuss some preliminaries.
In this section, we discuss the preliminary concepts of communities of web services and introduce the challenges behind community formation.

\subsection{Web Services}\label{s:ws}

In the recent years, online services have become a standard part of daily life around the globe. Many modern applications rely on web services from different providers. For instance, many mobile and tablet applications that have limited storage and processing power are merely aggregating information from different online services. Examples are vast, including weather forecasting, ticket selling, shopping apps, local maps and location services.

The World Wide Web Consortium (W3C) defines web services as ``software systems designed to support interoperable machine-to-machine interaction over a network. It has an interface described in a machine-processable format (specifically WSDL). Other systems interact with the web service in a manner prescribed by its description using SOAP messages, typically conveyed using HTTP with XML serialization in conjunction with other Web-related standards''. When developers declare a new web service, it will be
discovered based on its description, which fully discloses its functionalities. Developers also have to declare a public interface and a readable documentation to help other developers when integrating different services \cite{w3cwsdl}. Nowadays, web API, standards that do not require XML-based web service protocols like SOAP and WSDL are also emerging. They are called RESTful (representational state transfer) services, which are moving towards simpler communication protocols.
%They are not restricted
%to XML formats, recently JSON, a human readable and simpler format
%is becoming popular among online service providers.

We are not going to delve into the engineering details of online web service implementation and its protocols in this thesis. We are interested in web services from a business model perspective. Service providers usually charge end users for services they provide. For example, Google has listed pricing and plans for a wide range of services they provide on their web service console page\footnote{$https://code.google.com/apis/console$}.

As in other proposals \cite{journals/mags/BaldoniBM10,10.1109/TSC.2012.12,DBLP:conf/IEEEscc/KhosravifarABT11}, in this paper, we abstract web services as rational agents\footnote{The term rational is used here in the sense that web services are utility maximizers.} that provide services to end users. They aim to maximize their individual income  by receiving enough requests from end users. In order to increase their revenues, web services seek for more tasks if they have the capacity and throughput to do so. Web services can join communities to enhance efficiency by collaborating with others, to have access to broad market share, and for the opportunity to receive a bigger task pool from end users.
Furthermore, the high reliance on web services has resulted in increased quality expectations from end users. Communities of web services can provide higher availability, performance, reliability, and recovery for end users.

\subsection{Web Service Communities}\label{s:wsc}

The community of web services is essentially a virtual group of web services having similar functionalities \cite{DBLP:journals/ijebr/MaamarSTBB09}. Communities aggregate web services and communicate with other entities such as UDDI registries and users, using identical protocols to those used by single web services. Web services join communities to increase utility by having a larger market share and task pool. The community coordinator is responsible for securing the community, managing membership requests from web services and distributing user tasks among the community members. The coordinator tries to attract quality web services to join and keep the community as stable and productive as possible to gain better reputation and user satisfaction, which increases the community's market share. How web services reside within communities and how communities of web services are engineered is described comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}.

@@

Our plan for future work is to advance learning process on the training set that we provided in our work. SVN machine learning algorithm are suitable in classification of our training data set, to better classify correct or wrong decisions based on long-term utility gains, as data set outputs. This can further facilitate the process of finding optimal cooperators in regards to enhancing web services' overall performance as service providers.

>>>>

Given the dynamic and unpredictable nature of the Internet, delivering high quality services is a critical and challenging issue. One practical solution towards delivering such quality services is utilizing intelligent decision making agents. These agents aim at maximizing their gain by exploring the best ways to provide services that satisfy end users \cite{Zeng:2003:QDW:775152.775211, 10.1109/ARES.2008.7, Demirkan2013412, journals/tsc/ZhengZYB13, Josang:2007:STR:1225318.1225716}. However, agent-based web services are functionally limited in the sense that they cannot handle a large number of requests at the same time without compromising the quality of service provided. Recent developments have attempted to shift web services from simple models, consisting of individual components, to models made up of autonomous and group-based components that share common goals. In group-based models, interaction, composition, and cooperation are the key challenges that directly impact the group's overall performance in achieving common goals \cite{ICWS2011-1, SCC2011-1, journals/mags/BaldoniBM10, journals/jcss/CasadoYT13}. To that end, we see the emergence of web service \emph{communities}, which consist of grouping services with similar functionalities but distinct nonfunctional properties \cite{Zeng:2003:QDW:775152.775211, 10.1109/ARES.2008.7, Paik:2005:TSS:2229263.2230038, Medjahed05adynamic}. A community of web services runs continuous performance assessment functions that regulate web services' interactions and manage their composition and cooperation.

@@

\section{Challenging Issues}\label{s4:preliminaries}
%In this section, we first present the architecture of DDM. We explore the characteristics of intelligent service agents and the features we extract for training. To do this, we first discuss some preliminaries.
In this section, we introduce the challenges behind community formation.

@@

%Our plan for future work is to advance learning process on the training set that we provided in our work. SVN machine learning algorithm are suitable in classification of our training data set, to better classify correct or wrong decisions based on long-term utility gains, as data set outputs. This can further facilitate the process of finding optimal cooperators in regards to enhancing web services' overall performance as service providers.
